---
title: "Quadrilateral learning experiments"
author: "Andres Gomez Emilsson and Mike Frank"
date: "May 17, 2015"
output: html_document
---

Preliminaries.

```{r prelims}
rm(list=ls())
library(dplyr)
library(tidyr)
library(ggplot2)
library(binom)
library(lme4)
library(bootstrap)
library(magrittr)

## for bootstrapping 95% confidence intervals
theta <- function(x,xdata,na.rm=T) {mean(xdata[x],na.rm=na.rm)}
ci.low <- function(x,na.rm=T) {
  mean(x,na.rm=na.rm) - quantile(bootstrap(1:length(x),1000,theta,x,na.rm=na.rm)$thetastar,.025,na.rm=na.rm)}
ci.high <- function(x,na.rm=T) {
  quantile(bootstrap(1:length(x),1000,theta,x,na.rm=na.rm)$thetastar,.975,na.rm=na.rm) - mean(x,na.rm=na.rm)}

theme_set(theme_bw())
```

Load data.

```{r data_clean}
d1 <- read.csv("../data/experiment_1.tsv", header=TRUE, 
              sep="\t", row.names=NULL, stringsAsFactors = FALSE)
d2 <- read.csv("../data/experiment_2.tsv", header=TRUE, 
               sep="\t", row.names=NULL, stringsAsFactors = FALSE)

rd <- bind_rows(d1, d2)
```

Constants:

* Are all squares parallelograms?
* Are all squares rectangles?
* Are all squares also rhombuses?
* Are all rectangles also parallelograms?
* Are all rectangles also rhombuses?
* Are all rectangles also squares?
* Are all rhombuses also parallelograms?
* Are all rhombuses also rectangles?
* Are all rhombuses also squares?
* Are all parallelograms also rectangles?
* Are all parallelograms also rhombuses?
* Are all parallelograms also squares?

```{r}
correct_answers <- c(0, 0, 0, 0, 1, 1, 0, 1, 1, 1, 1, 1)

questions <- c("sp", "sr", "sh", "rp", "rh", "rs",
                      "hs", "hr", "hp", "ps", "pr", "ph")

related <- list(square = c(1, 2, 3, 6, 9, 12), 
                rectangle = c(2, 4, 5, 6, 8, 10),
                rhombus = c(3, 5, 7, 8, 9, 11),
                parallel = c(1, 4, 7, 10, 11, 12))
```

Data cleaning
-------------

* shape numbers: 0 square, 1 rectangle, 2 rhombus, 3 parallelogram
* conditions: 3 Active learning, 4 Passive learning, 5 Baseline condition


```{r}
d <- rd %>% 
  select(workerid, starts_with("Answer")) %>%
  rename(pre = Answer.pretest_responses,
         post = Answer.posttest_responses,
         time = Answer.training_time, 
         shape = Answer.shape_of_focus,
         cond = Answer.training_regime) %>%
  select(-starts_with("Answer")) %>%
  rowwise %>%
  do(data.frame(workerid = .$workerid, 
                pre = as.integer(strsplit(substr(.$pre, 2, 24),
                                                  ",")[[1]]),                
                post = as.integer(strsplit(substr(.$post, 2, 24),
                                                  ",")[[1]]),
                time = .$time, 
                qnum = 1:12,
                cond = .$cond,
                shape = .$shape)) %>%
  gather(phase, resp, pre, post) %>%
  mutate(cond = factor(cond, 
                       levels = c(3,4,5), 
                       labels = c("active", "teaching", "baseline")),
         shape = factor(shape, 
                        levels = c(0, 1, 2, 3), 
                        labels = c("square","rectangle","rhombus","parallel")),
         question = questions[qnum], 
         answer = correct_answers[qnum],
         correct = resp == answer) %>%
  rowwise() %>%
  mutate(relevant = qnum %in% related[shape][[1]])
```

Analysis
--------

Between subjects

```{r}
ms <- d %>% 
  group_by(cond, shape, phase, question, relevant) %>%
  summarise(m.cih = ci.high(correct),
            m.cil = ci.low(correct),            
            m = mean(correct))

qplot(question, m, fill = phase, 
      ymin = m - m.cil, ymax = m + m.cih,
      position = position_dodge(width = .9),
      alpha = relevant, 
      facets = shape ~ cond, 
      data = ms,       
      geom = c("bar", "linerange"), stat = "identity") 
```

Within subjects change scores

```{r}
ms <- d %>% 
  select(-resp) %>% 
  spread(phase, correct) %>%  
  group_by(cond, shape, question, relevant) %>%
  summarise(m.cih = ci.high(post - pre),
            m.cil = ci.low(post - pre),            
            m = mean(post - pre))

qplot(question, m, fill = relevant,
      ymin = m - m.cil, ymax = m + m.cih,
      position = position_dodge(width = .9),
      facets = shape ~ cond, 
      data = ms,       
      geom = c("bar", "linerange"), stat = "identity") 
```

Within subjects but aggregated across questions

```{r}
ms <- d %>% 
  select(-resp) %>% 
  spread(phase, correct) %>%  
  group_by(workerid, cond, shape, relevant) %>%
  summarise(m = mean(post - pre)) %>%
  group_by(cond, shape, relevant) %>%
  summarise(m.cih = ci.high(m),
            m.cil = ci.low(m),
            m = mean(m), 
            n = n())

qplot(cond, m, fill = relevant,
      ymin = m - m.cil, ymax = m + m.cih,
      position = position_dodge(width = .9),
      facets = . ~ shape, 
      data = ms,       
      geom = c("bar", "linerange"), stat = "identity")
```

Basic analysis over all questions - pretest only. Sanity check that we are getting reasonable answers?

```{r}
ms <- d %>% 
  filter(phase == "pre") %>%
  group_by(workerid, question) %>%
  summarise(m = mean(correct)) %>%
  group_by(question) %>%
  summarise(m.cih = ci.high(m),
            m.cil = ci.low(m),
            m = mean(m))

qplot(question, m, 
      ymin = m - m.cil, ymax = m + m.cih,
      position = position_dodge(width = .9),
      data = ms,       
      geom = c("bar", "linerange"), stat = "identity") + 
  geom_hline(yintercept = .5, lty = 2)
```