---
title: "Quadrilateral Models"
author: "Andres Gomez Emilsson"
date: "May 8, 2015"
output: html_document
---


```{r prelims}
library(dplyr)
library(tidyr)
library(ggplot2)
library(binom)
library(lme4)
```


```{r data_clean}
d <- read.csv("experiment_1.tsv", header=TRUE, sep="\t", row.names=NULL, stringsAsFactors = FALSE)
n_participants <- length(d$Answer.training_regime)

pre_and_post_responses <- NULL

for (i in 1:length(d$Answer.training_regime)){
  pre_responses <- d$Answer.pretest_responses[i]
  pre_responses <- substr(pre_responses, 2, 24)
  pre_values <- as.integer(strsplit(pre_responses, ",")[[1]])
  
  post_responses <- d$Answer.posttest_responses[i]
  post_responses <- substr(post_responses, 2, 24)
  post_values <- as.integer(strsplit(post_responses, ",")[[1]])
  
  values <- c(pre_values, post_values)
  
  pre_and_post_responses <- rbind(pre_and_post_responses, values)
}

relevant_df <- data.frame(pre_and_post_responses)
colnames(relevant_df) <- c("pre_1", "pre_2", "pre_3", "pre_4", "pre_5", "pre_6", "pre_7", "pre_8", "pre_9", "pre_10", "pre_11", "pre_12", "post_1", "post_2", "post_3", "post_4", "post_5", "post_6", "post_7", "post_8", "post_9", "post_10", "post_11", "post_12")


# Condition 
relevant_df$condition <- d$Answer.training_regime
relevant_df$time <- d$Answer.training_time

```

Question order:

Are all squares parallelograms?
Are all squares rectangles?
Are all squares also rhombuses?
Are all rectangles also parallelograms?
Are all rectangles also rhombuses?
Are all rectangles also squares?
Are all rhombuses also parallelograms?
Are all rhombuses also rectangles?
Are all rhombuses also squares?
Are all parallelograms also rectangles?
Are all parallelograms also rhombuses?
Are all parallelograms also squares?


```{r answer_means}
correct_responses <- c(0, 0, 0, 0, 1, 1, 0, 1, 1, 1, 1, 1)
rhombus_related <- c(3, 5, 7, 8, 9, 11)

relevant_df$pre_correct <- 1:n_participants*0
relevant_df$post_correct <- 1:n_participants*0
relevant_df$pre_rhombus_related <- 1:n_participants*0
relevant_df$post_rhombus_related <- 1:n_participants*0
for (i in 1:length(relevant_df$condition)) {
  relevant_df$pre_correct[i] <- sum(correct_responses == relevant_df[i,1:12])
  relevant_df$post_correct[i] <- sum(correct_responses == relevant_df[i,13:24])
  relevant_df$pre_rhombus_related[i] <- sum(correct_responses[rhombus_related] == relevant_df[i,rhombus_related])
  relevant_df$post_rhombus_related[i] <- sum(correct_responses[rhombus_related] == relevant_df[i,(rhombus_related + 12)])
}

relevant_df$correct_delta <- relevant_df$post_correct - relevant_df$pre_correct
relevant_df$rhombus_delta <- relevant_df$post_rhombus_related - relevant_df$pre_rhombus_related



means_by_condition <- answers_by_odd_one_kind <- aggregate(cbind(pre_11, post_11, pre_rhombus_related, post_rhombus_related, pre_correct, 
                                                                 post_correct, correct_delta, time) ~ 
                             condition, data=relevant_df, mean)

means_by_condition


summary(lm(rhombus_delta ~ as.factor(condition), data = relevant_df))

```


